Meta RL analyses

### 2019-02-28 meta_RL_analyses.Rmd
Fix

```{r}
ggplot(language_d %>%
         filter(epoch == 0,
                is_new_game),
       aes(x=named_run_type, y=reward, fill=as.factor(run))) +
  geom_hline(yintercept=0.,
             linetype=2,
             alpha=0.5) +
  geom_violin(position="dodge") +
  geom_point(aes(group=as.factor(run)),
             size=3,
             stat="summary", fun.y="mean",
             position=position_dodge(width=0.9)) +
  scale_color_brewer(palette="Set2") + 
  ylim(-0.6, 0.6) +
  labs(x="Run type",
       y="Reward density") + 
  guides(fill=guide_legend(title="Run"))
ggsave("writing/figures/language_basic_by_run.png", width=5, height=3.5)
```

>>>>

```{r}
ggplot(language_d %>%
         filter(epoch == 0,
                is_new_game),
       aes(x=run, y=reward, fill=as.factor(run))) +
  geom_hline(yintercept=0.,
             linetype=2,
             alpha=0.5) +
  geom_violin(position="dodge") +
  geom_point(aes(group=as.factor(run)),
             size=3,
             stat="summary", fun.y="mean",
             position=position_dodge(width=0.9)) +
  scale_color_brewer(palette="Set2") + 
  ylim(-0.6, 0.6) +
  labs(x="Run",
       y="Reward density on held-out tasks") + 
  guides(fill=guide_legend(title="Run")) +
  facet_wrap(~named_run_type)
ggsave("writing/figures/language_basic_by_run.png", width=5, height=3.5)
```
